Title

### 2014-11-14 manuscript.tex
Introduction to the implementation section

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\address{
\footnotemark[1] Universidade do Estado do Rio de Janeiro,
Rio de Janeiro, Brazil.
\\
\footnotemark[2] Observat\'orio Nacional,
Rio de Janeiro, Brazil.
\\
\footnotemark[3] Department of Mathematics and Geosciences,
University of Trieste, Trieste, Italy.
}

@@

@@

>>>>

@@

\address{
\footnotemark[1]Universidade do Estado do Rio de Janeiro,
Rio de Janeiro, Brazil.
email: leouieda@gmail.com
\\
\footnotemark[2]Observat\'orio Nacional,
Rio de Janeiro, Brazil.
\\
\footnotemark[3]Department of Mathematics and Geosciences,
University of Trieste, Trieste, Italy.
}

@@

The calculation of the tesseroid gravitational fields with adaptive
discretization is implemented in the open-source package \textit{Tesseroids}.

Tesseroids is freely available under the BSD 3-clause free-software license.

An archived version of the source code is available along with this article.

The latest version can be downloaded from the official
website\footnote{http://www.leouieda.com/tesseroids}.

Ongoing development takes place through the source code hosting site
Github\footnote{https://github.com/leouieda/tesseroids}.

\textit{Tesseroids} is written in the C programming language.

Tesseroids consists of command-line programs.

Tesseroids tries to follow the Unix principals of
(1) making each program do one thing well,
(2) using plain text for input and output,
(3) making each program a ``filter'' that can be used in conjunction with other
programs.

The gravitational potential, attraction, and Marussi tensor components
are each computed by a separate program.

Programs for model and computation grid generation are also included.

The package also includes programs for computing the gravitational fields of
right rectangular prisms in Cartesian and spherical coordinates.

Tesseroids programs receive input through command-line arguments and the
standard input channel (STDIN) and output the results through
the standard output channel (STDOUT).

The command-line interface of each program was designed so that they
can be called in sequence using a Unix pipe.

For example, the command to
generate a regular grid with $NLON \times NLAT$ points,
calculate on it the $g_z$ and $g_{zz}$ caused by the tesseroids in file
MODELFILE,
and save the results to a file called OUTPUT
is:

\begin{verbatim}
tessgrd -rW/E/S/N -bNLON/NLAT -zHEIGHT | \
    tessgz MODELFILE | \
    tessgzz MODELFILE > OUTPUT
\end{verbatim}

The \texttt{src} folder of the distribution archive
contains the \texttt{.c} files that build the command-line programs.

The \texttt{src/lib} folder contains the source files that implement the
numerical computations.

We will not describe here the implementation of the input/output parsing and
other miscellanea.

Instead, we will focus on the details of the Gauss-Legendre Quadrature
integration of equations~\ref{eq:tesspot},~\ref{eq:tessgrav},
and~\ref{eq:tesstensor}
and the adaptive discretization of tesseroids.

\subsection{Numerical integration}

The first step in the numerical integration with the GLQ is to compute the
locations of the point masses (i.e., the discretization points).

These points are roots of Legendre polynomials.

We use the

\subsection{Implementation of adaptive discretization}
